%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Using hiReadsProcessor}

## Introduction
`hiReadsProcessor` contains set of functions which allow users to process LM-PCR products sequenced using any platform. Given an excel/txt file containing parameters for demultiplexing and sample metadata, the functions in here automate trimming of adaptors, remove any vector sequence, and identify host genomic location. In addition, if INSPIR&D MySQL database is setup, the sequence attrition is loaded into respective tables for post processing setup and analysis.

Below are few simple steps to get you started.

## Quick *hiReadsProcessor* tutorial.

### Step 1: Loading the tools
First load this package and the parallel backend of choice from `BiocParallel` library. Although `BiocParallel` is imported internally and will invoke `multicore` like functionality, you may have to load it to invoke `snow` like functionality.
```{r}
library(hiReadsProcessor)
```

### Step 2: Processing the data
The package comes with example 454 sequencing run: `FLX_sample_run`. In the rest of this tutorial we will use this dataset to 

```{r}
```

## Detailed *hiReadsProcessor* tutorial.

### Sequencing Run related functions
read.SeqFolder
read.sampleInfo
read.seqsFromSector
findBarcodes|decodeByBarcode
findPrimers
findLTRs
findVector
findLinkers
troubleshootLinkers
write.runData

### Reads related functions
splitByBarcode
dereplicateReads
replicateReads
splitSeqsToFiles
write.listedDNAStringSet
trimSeqs
removeReadsWithNs

### Alignment functions
startgfServer
stopgfServer
blatSeqs
blatListedSet
subreadAlignSeqs
vpairwiseAlignSeqs
pairwiseAlignSeqs
primerIDAlignSeqs

### Alignment related functions
read.psl
write.psl
read.blast8
read.BAMasPSL
pairUpAlignments

### Integration Site functions
findIntegrations
getIntegrationSites
clusterSites
getSonicAbund
isuSites
otuSites
otuSites2
crossOverCheck

### Utility functions
findAndTrimSeq
summary.elegant
summary.simple
pslToRangedObject
pslCols
getSectorsForSamples
extractSeqs
extractFeature
doRCtest
chunkize
addFeature
addListNameToReads